Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-10 acknowledgments.tex
updated acknowledgments.

Development of \enzo\ has been supported by the National Science Foundation, the National Aeronautics and Space Administration, the Department of Energy, the University of Illinois and National Center for Supercomputing Applications, UC San Diego and the San Diego Supercomputing Center, Columbia University, Georgia Tech, Michigan State University, ...  \red{We all need to add to the acknowledgments!}

>>>>

Development of \enzo\ has been ongoing since 1994 by a wide range of
agencies and institutions.  In all grants listed, we put the
initials of the PI (if an \enzo\ developer) or the \enzo\ developer
funded by the grant (if the PI is not a developer of \enzo).

This work has been supported by the National Science Foundation by
grants
AAG-0808184 (DRR),
AAG-1109008 (DRR),
ACI-9619019 (MLN),
ASC-9313135 (MLN),
AST-9803137 (MLN), 
AST-0307690 (MLN), 
AST-0407176 (RC),
AST-0407368 (SS, EJH),
AST-0507521 (RC) 
AST-0507717 (MLN), 
AST-0507768 (AK),
AST-0607675 (AK)
AST-0702923 (EJH),
AST-0707474 (BDS), 
AST-0708960 (MLN), 
AST-0807215 (JB),
AST-0808184 (MLN, AK),
AST-0908819 (BWO) 
AST-0955300 (NG),
AST-1008134 (GB) 
AST-1009802 (JSO), 
AST-1102943 (MLN)
AST-1106437 (JB),
AST-1210890 (GB),
AST-1211626 (JW),
OCI-0832662 (BWO, MLN),
OCI-0941373 (BWO),
PHY-1104819 (MLN, JB),
the CI TraCS fellowship (OCI-1048505; MJT),
and the Graduate Research Fellowship program (NG; SJS).

This work has been supported by the National Aeronautics and Space
Administration through grants
NAGW-3152 (MLN),
NAG5-3923 (MLN),
NNX08AH26G (MLN),
NNX09AD80G (BWO),
NNX12AH41G (GB),
NNX12AC98G (BWO),
NNZ07-AG77G (BDS),
NNG05GK10G (RC),
ATP09-0094 (SVL),
Chandra Theory grant \#TM9-0008X (BWO),
Hubble Space Telescope Theory Grant HST-AR-10978.01 (BDS),
Fermi Guest Investigator Program (\#21077; BWO),
and the Hubble Postdoctoral Fellowship through the Space Telescope Science
Insititue (120-6370; JW).

This work has been supported by the Department of Energy via
Los Alamos National Laboratory (LANL) Laboratory Directed Research and
Development Program (BWO, DCC, HX), 
the LANL Institute for Geophysics and Planetary Physics (BWO, DCC),
Los Alamos National Lab Director's Fellowship (No. DE-AC52-06NA25396;
BWO and DCC), and the
DOE Computational Science Graduate Fellowship (DE-FG02-97ER25308; SJS)

Additional financial support for the \enzo\ code has come from
Canada's NSERC through the USRA and CGS programs (EL) and through a 
Japan MEXT grant for the Tenure Track System (EJT).

We acknowledge the  many institutions that have supported \enzo\
development, including (in alphabetical order)
the
Columbia University,
Georgia Tech,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University
 the San Diego Supercomputing Center (through the Strategic Applications
Partner program and the Director’s office),
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  Stanford University,
University of Arizona,
University of Califoria at San Diego, 
 University of Florida,
the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara and the Aspen Center for Physics, who
generously hosted \enzo\ developers.

Computational resources for \enzo\ development have come from the NSF
XSEDE program, NASA high performance computing, the DOE INCITE
program, and the DOE Advanced Simulation and Computing (ASC) program.

The \enzo\ collaboration would also like to acknowledge the significant contributions to
\enzo\ development made by the late Dr. Robert P. Harkness.
